\pkg{cleanR}: Maid for Cleaning Datasets in \proglang{R}

### 2016-12-20 latex/article_vol2.tex

  We describe an \proglang{R} package which implements an extensive
  and customizeable suite of quality assessment tools to be applied to
  a dataset in order to identify potential problems in its
  variables. The results can be presented in an auto-generated,
  non-technical, stand-alone overview document, intended to be perused
  by an investigator with an understanding of the variables in the
  data and the experimental design, but not necessarily knowledge of
  \R{R}. Thereby, \pkg{cleanR} aids the dialogue between data
  analysist and field experts, while also providing easy
  documentation of reproducible data cleaning steps and data quality
  control. Moreover, the \pkg{cleanR} solution changes the data
  cleaning process from the usual ad hoc approach to a systematic,
  well-documented endeavor.  \pkg{cleanR} also provides a suite of
  more typical \proglang{R} tools for interactive data quality
  assessment and -cleaning. \hl{Hvad henvises der til med denne
    sætning?}

>>>>

  We describe an \proglang{R} package which implements an extensive
  and customizeable suite of quality assessment tools to be applied to
  a dataset in order to identify potential problems in its
  variables. The results can be presented in an auto-generated,
  non-technical, stand-alone overview document, intended to be perused
  by an investigator with an understanding of the variables in the
  data and the experimental design, but not necessarily knowledge of

  \R{R}. Thereby, \pkg{cleanR} aids the dialogue between data
  analysists and field experts, while also providing easy
  documentation of reproducible data cleaning steps and data quality
  control. Moreover, the \pkg{cleanR} solution changes the data
  cleaning process from the usual ad hoc approach to a systematic,
  well-documented endeavor.  \pkg{cleanR} also provides a suite of
  more typical \proglang{R} tools for interactive data quality
  assessment and -cleaning. \hl{Hvad henvises der til med denne
    sætning?}
